Precision calculations for cosmic shear

### 2017-02-08 discussion.tex
MK edit discussion

\citet{CFHTLenS-2pt-notomo} present a detailed comparison of cosmological
constraints obtained from a range of different two-point shear statistics
including the shear correlation function, $\xi_\pm$, the aperture-mass
dispersion, $\langle M_ {\rm ap} \rangle ^2$ \citep{1998MNRAS.296..873S}, and
the COSEBIs, $E_n$ \citep{COSEBIs}.  These statistics are linearly related to
the power spectrum via integrals of the form,
%
\begin{align}
%\label{eqn:integ}
& E_n =\int_0^{\infty}\frac{\d \ell \ell}{2\pi} W_n(\ell) P(\ell)\;,\\ \nonumber
& \langle M_ {\rm ap} \rangle ^2(\theta)=\int_0^{\infty}\frac{\d \ell \ell}{2\pi} U^2_\theta(\ell) P(\ell)\;,
\end{align}
%
where $W_n(\ell)$ and $U^2_\theta(\ell)$ are defined in \cite{COSEBIs} and
\cite{1998MNRAS.296..873S}. The corresponding equations for $\xi_\pm$ are given
in equation~\ref{eqn:xiGG}. Figure~\ref{fig:filters} shows the integrands of
these statistics for two cases, normalised to their maximum value, where the
integrands are of the form $\ell F(\ell) P(\ell)$. For $\xi_\pm$, $P(\ell)$ is
equal to the sum of the E and B-mode power spectra, motivating the development
of the aperture-mass dispersion statistic, $\langle M_ {\rm ap} \rangle ^2$.
This statistic is, however, a lossy conversion and is biased by small angular
separations, where blending of galaxies makes shear measurement challenging
\citep{KSE06}.  The COSEBIs statistic tackles both these
shortcomings.  The upper two panels of figure~\ref{fig:filters} show the
integrands\footnote{Note that the lower left panel of Fig.~1 in
\citet{2016arXiv161104954K} shows an integrated form of this function for a
maximum angular separation of $100^\prime$. However, in \citet{CFHTLenS-2pt-notomo},
the data used in \citet{2016arXiv161104954K}, $\theta$ is between $0.8'$ and
$350'$.} of $\xi_\pm$ for $\theta=100'$ and $\theta=350'$. The lower middle
panel in Figure~\ref{fig:filters} shows the COSEBIs integrands for two angular
ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for
the lowest COSEBIs mode, $E_1$, as the higher modes generally probe larger
$\ell$-modes.  Finally, the lowest panel shows the integrands of aperture mass
dispersion statistics, for the same two maximum angular ranges.

>>>>

\citet{CFHTLenS-2pt-notomo} present a detailed comparison of cosmological
constraints obtained from a range of different two-point shear statistics
including the shear correlation function, $\xi_\pm$, the aperture-mass
dispersion, $\langle M_ {\rm ap}^2 \rangle2$ \citep{1998MNRAS.296..873S}, and
the COSEBIs, $E_n$ \citep{COSEBIs}.  These statistics are linearly related to
the shear power spectrum in the flat-sky approximation via integrals of the form (omitting tomographic indices),
%
\begin{align}
  \langle M_ {\rm ap}^2 \rangle(\theta) & = \int_0^{\infty}\frac{\d \ell \ell}{2\pi}
  \hat U^2(\theta\ell) P^\gamma(\ell),
  \label{eqn:integ}
  \\
  E_n & = \int_0^{\infty}\frac{\d \ell \ell}{2\pi} W_n(\ell) P^\gamma(\ell),
\end{align}
%
where the Fourier-space filter functions $\hat U$ and $W_n$ are defined in
\cite{1998MNRAS.296..873S} and \cite{COSEBIs}. The corresponding equations for
$\xi_\pm$ are given in equation~\ref{eqn:xiGG}. Figure~\ref{fig:filters} shows
the integrands of these statistics for two cases, normalised to their maximum
value, where the integrands are of the form $\ell F(\ell) P^\gamma(\ell)$. For
$\xi_\pm$, $P^\gamma(\ell)$ is equal to the sum of the E and B-mode power spectra
which cannot easily be separated,
motivating the development of the aperture-mass dispersion statistic, $\langle
M_ {\rm ap}^2 \rangle$. This statistic is, however, a lossy conversion and is
biased by small angular separations, where blending of galaxies makes shear
measurement challenging \citep{KSE06}. The COSEBIs statistic tackles both
these shortcomings.  The upper two panels of figure~\ref{fig:filters} show the
integrands\footnote{Note that the lower left panel of Fig.~1 in
\citet{2016arXiv161104954K} shows an integrated form of this function for a
maximum angular separation of $100^\prime$. However, in
\citet{CFHTLenS-2pt-notomo}, the data used in \citet{2016arXiv161104954K},
$\theta$ is between $0.8'$ and $350'$.} of $\xi_\pm$ for $\theta=100'$ and
$\theta=350'$. The lower middle panel in Figure~\ref{fig:filters} shows the
COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where
we only show the integrands for the lowest COSEBIs mode, $E_1$, as the higher
modes generally probe larger $\ell$-modes.  Finally, the lowest panel shows the
integrands of aperture mass dispersion statistics, for the same two maximum
angular ranges.
